\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-10 Thesis.tex
much added to 4

\section{Towards a More Effective Presentation Format}
\label{sec:TowardsAMoreEffectivePresentationFormat}
\ednote{is relatively shallow, about the implementation we only get to know that it is in Java. An architecture diagram would be helpful, and if you have that, you can explain it. That will give you something to guide the level of presentation.}

\ednote{screenshot hack?}

@@

\sys itself operates in five main steps:\\
\vspace{-12pt}
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item Get user input for the location and names of folders.
\item Parse \sTeX to retrieve the order of slides.
\item Extract dependencies from relationanl info.
\item Extract necessary XHTML or PDF parts for slides.
\item Create presentation.
\end{enumerate}
\vspace{5pt}

@@

For including the XHTML or the PNGs we use self-created boilerplate code, in which only some coordinates and the XHTML or the PNGs for the slide are added. The exact details of this process will be explained in more detail in sections \ref{sec:narrativePaths}, \ref{sec:levels}, \ref{sec:orderedInfoGraphs}, and \ref{sec:RelationalPresentations}. \ednote{check}\\

@@

The information graphs that OMDoc provides us with could also be simply visualized as a tree of information. But this would not be very engaging and it would be hard for a person to process. Similarly, traditional slide-based presentations do not provide a very engaging or interactive form of presenting information. Therefore we will focus on using spatial narrative to make presentations more engaging and enhance knowledge transfer.\\

@@

In our system \sys, we parse the \stex files to retrieve the traditional narrative the writer intended to use. This is the first narrative layer, which we will refer to as a \textit{primary narrative path} since we go from slide to slide on our path to the end of the presentation. To create this primary narrative path we need to add several slides with increasing x-coordinates as shown in \autoref{fig:narrativePathCode}. This code snippet creates the narrative path portrayed in \autoref{fig:primaryNarrativePath}.\\

@@

The primary narrative path is the traditional path a presenter normally uses when preparing a PowerPoint presentation. This path happens to also contain temporal information which is illustrated by the arrow in \autoref{fig:primaryNarrativePath}. This temporal information is what we extracted from the \stex as the order in which the slides (or the information on the slides) should appear in.\\

@@

@@

\ednote{Refer back to status of information within ... later on refer to this with the different levels.}

When writing a document or course notes in \stex, the creator general writes a top-level file such as \textit{notes.tex} from where other tex-files are included. These included files again include further tex-files etc.. Thus we are automatically provided with levels that we can use for splicing our primary narrative path into smaller narrative paths. In essence, on any level the order of information in that topic is a narrative path.\\

\begin{wrapfigure}{c}{\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.97\textwidth]{assets/final/inclusionGraphPythagorean}
    } 
\vspace{-5pt}
  \caption{Inclusion Graph for the Pythagorean Theorem}
  \label{fig:inclusionGraph}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

@@

The graph for CS looks more like this:

\begin{wrapfigure}{c}{\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.3\textwidth]{assets/final/inclusionGraphCS}
    } 
\vspace{-5pt}
  \caption{Inclusion Graph for Gen CS}
  \label{fig:inclusionGraph}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

\begin{wrapfigure}{c}{\textwidth}
\vspace{-50pt}
\end{wrapfigure}
sda

\subsection{Ordered Information Graphs}
\label{sec:orderedInfoGraphs}
\ednote{needs work}

The Local MathHub Tool (lmh) outputs information about dependencies of topics as shown below in \autoref{fig:reldatacode}. \\

\begin{wrapfigure}{r}{\textwidth}
\vspace{-26pt}
\begin{minted}[linenos=true, bgcolor=bg]{C}
theory path/to/file?theory_name
Includes path/to/file path/to/dependent/file?theory_name
\end{minted}
\vspace{-5pt}
  \caption{Code Snippet of Relational Data}
  \label{fig:reldatacode}
  \vspace{12pt}
\end{wrapfigure}

@@

\ednote{add example}

@@

The system \sys parses the output and thus retrieves the dependencies of the topics. Combining this information with the order in which these pieces of information occur, i.e. with narrative paths and levels, we will be able to create ordered information graphs that allow users to interact with the presentation.

@@

\ednote{draw the whole graph and add here}

\ednote{add example in slides and explain the different layers again}

\ednote {explain ids of slides}

\ednote{introduce information graphs}

\ednote{structuring of the presentation - link with primitives and spatial narrative}

\ednote{note to self: status of information -> levels}

\subsection{The Relational Presentations}
\label{sec:RelationalPresentations}
\ednote{needs work}
\ednote{refer back to primitives: However, the relations can be much more expressive within impress.js.}

@@

With the information about the order and the dependencies of information within the paper, \sys automatically creates a presentation by parsing the XHTML the created from the OMDocs which is then parsed and added to a presentation file. Each xhtml file represents its own slide and is hence put into its own div as shown in section \ref{sec:Impressjs}. The primary narrative that the presenter wants to follow is formed by a horizontal stream of slides. \ednote{add picture of this}\\

This horizontal stream of slides is achieved by giving the slides incremental \texttt{data-x} values in the attributes. If a slide has dependencies then these will be added as slides below the slide itself. This, in turn, is achieved by keeping the \texttt{data-x} value but increasing the \texttt{data-y} value. Thus users can now simply press down and explore all the dependent information.\\

%impress.js gives us all the necessary primitives that were outlined in section \ref{sec:primitives}. Therefore it will give us the perfect environment to transform the XML data that OMDoc provides us with into an interactive presentation. In this step we will define several models of how data is presented within a frame. Next we will automate that the different frames have different sizes according to the importance of the presented information (see section \ref{sec:inforep}). Last but not least we need to create several models of how the temporal and dependency relations between the different frames can be portrayed within impress.js.\\

%Once we have an ordered information graph with all the additional attribute values mentioned in section \ref{sec:wp2}, we will create the knowledge presentation system \sys. \sys will visualize the information from the graph including all the attributes we added. The outcome of this part should be a general \sys presentation model, that implements the models according to the models chosen in section \ref{sec:wp1}. We will then use \sys to visualize information in WP4.\\

\ednote{show possible paths thru presentation}

@@

\subsection{General Evaluation}

@@

\subsection{Shortcomings and Problems with the System}

>>>>

\section{Towards a More Effective Presentation Format}
\label{sec:TowardsAMoreEffectivePresentationFormat}
\ednote{screenshot hack?}

@@

\sys itself operates in five main steps:\\
\vspace{-12pt}
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item Get user input for the location and names of folders.
\item Parse \sTeX to retrieve the order of slides.
\item Extract dependencies from relational info.
\item Extract necessary XHTML or PDF parts for slides.
\item Create presentation.
\end{enumerate}
\vspace{5pt}

@@

For including the XHTML or the PNGs we use self-created boilerplate code, in which only some coordinates and the XHTML or the PNGs for the slide are added. The exact details of this process will be explained in more detail in subsection \ref{sec:RelationalPresentations}. To complement the HTML, a CSS stylesheet is added which adds the Jacobs logo. The design of the template is based on a presentation by Sebastian Wolf's \cite{Wolf:npentrel15}. \ednote{check subsections}\\

@@

The information that OMDoc provides us with could also be simply visualized as a tree of information. But this would not be very engaging and it would be hard for a person to process. Similarly, traditional slide-based presentations do not provide a very engaging or interactive form of presenting information. Therefore we will focus on using spatial narrative to make presentations more engaging and enhance knowledge transfer.\\

@@

\begin{wrapfigure}{c}{\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.97\textwidth]{assets/final/inclusionGraphPythagorean}
    } 
\vspace{-16pt}
  \caption{Inclusion Graph for the Pythagorean Theorem}
  \label{fig:inclusionGraph}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

\begin{wrapfigure}{l}{0.3\textwidth}
\vspace{-12pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.28\textwidth]{assets/final/inclusionGraphCS}
    } 
\vspace{-16pt}
  \caption{Inclusion Graph for GenCS}
  \label{fig:inclusionGraphGenCS}
\vspace{-24pt}
  \end{center}
\end{wrapfigure}

In our system \sys, we parse the \stex files using a Depth First Search algorithm to retrieve the traditional narrative the writer intended to use. For the explanation of the pythagorean theorem this can be seen in \autoref{fig:inclusionGraph}. The graph for a whole course like the General Computer Science course (GenCS) at Jacobs University Bremen \cite{Kohlhase:GenCSII:base} is too big to be shown properly (see \autoref{fig:inclusionGraphGenCS}).\\

The retrieved order is the intended narrative layer, which we will refer to as a \textit{primary narrative path} since we go from slide to slide on our path to the end of the presentation. To create this primary narrative path we need to add several slides with increasing x-coordinates as shown in \autoref{fig:narrativePathCode}. This code snippet creates the narrative path portrayed in \autoref{fig:primaryNarrativePath}.\\

@@

The primary narrative path, formed by a horizontal stream of slides, is the traditional path a presenter normally uses when preparing a PowerPoint presentation. This path happens to also contain temporal information which is illustrated by the arrow in \autoref{fig:primaryNarrativePath}. This temporal information is what we extracted from the \stex as the order in which the slides (or the information on the slides) should appear in.\\

@@

\ednote{how to add a slide!}
by parsing the XHTML the created from the OMDocs which is then parsed and added to a presentation file. Each xhtml file represents its own slide and is hence put into its own div as shown in section \ref{sec:Impressjs}. \ednote{add picture of this}\\

@@

When writing a document or course notes in \stex, the creator general writes a top-level file such as \textit{notes.tex} from where other tex-files are included. These included files again include further tex-files etc.. Thus we are automatically provided with levels that we can use for splicing our primary narrative path into smaller narrative paths. In essence, on any level the order of information in that topic is a narrative path. In mathematical notation a level within a directed graph $G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the set of directed edges, is the set $L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$. From these levels we can infer the status of the information. Anything that is on the same level or in the sublevels thereof is generally considered to be \textit{course-old} information.\\

\begin{wrapfigure}{c}{\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.97\textwidth]{assets/final/levels}
    } 
\vspace{-5pt}
  \caption{Inclusion Graph with Levels}
  \label{fig:levelsGraph}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

@@

With the information about the order and the dependencies of information within the paper, \sys automatically creates a presentation. It does this incrementally. As outlined in \autoref{sec:narrativePaths} and visible in \autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order of the slides. After adding each slide it checks whether there is \textit{course-ancient} information, i.e. whether there are dependencies, for that slide. If there are dependencies those are added below the slide itself (see \autoref{fig:visualDependency}). This is achieved by keeping the \texttt{data-x} value but increasing the \texttt{data-y} value. \ednote{code snippet}\\

\subsection{Ordered Information Graphs}
\label{sec:orderedInfoGraphs}

As described in \autoref{sec:TowardsAMoreEffectivePresentationFormat}, lmh outputs information about dependencies of topics. The general format of one relation can be seen in \autoref{fig:reldatacode} (lines 1-2). A specific example showing some of the dependencies for the pythagorean theorem example can be seen in lines 4-11.\\

\begin{wrapfigure}{r}{\textwidth}
\vspace{-26pt}
\begin{minted}[linenos=true, bgcolor=bg]{C}
theory path/to/file?theory_name
Includes path/to/file path/to/dependent/file?theory_name

theory 
pythagoreantheorem/pythagoreantheorem/theorem.omdoc?pythagoreantheorem
Includes 
pythagoreantheorem/pythagoreantheorem/theorem.omdoc?pythagoreantheorem
pythagoreantheorem/measurements/right_angle.omdoc?right_angle
Includes 
pythagoreantheorem/pythagoreantheorem/theorem.omdoc?pythagoreantheorem
pythagoreantheorem/measurements/area.omdoc?angle
\end{minted}
\vspace{-5pt}
  \caption[Caption for LOF]{Code Snippet of Relational Data \footnotemark}
  \label{fig:reldatacode}
  \vspace{12pt}
\end{wrapfigure}

@@

\footnotetext{All the above paths were shortened by "http://mathhub.info/MiKoMH/" to maintain readability.}

The system \sys parses the relational data and thus retrieves the dependencies of the topics. We already know that the level a piece of information is associated with infers that it is \textit{course-old} information. Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information that happened more time ago.\\

@@

Combining this information with the order in which these pieces of information occur, i.e. with narrative paths and levels, we now have an ordered information graph out of which we can build a presentation that Annie can interact with to learn about the pythagorean theorem. We will look at this graph in the presentation in \autoref{sec:RelationalPresentations}.

\begin{wrapfigure}{c}{\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.97\textwidth]{assets/final/dependencyGraphPythTheo}
    } 
\vspace{-5pt}
  \caption{Dependency Graph}
  \label{fig:depGraphPythagoreanFull}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

\subsection{The Relational Presentation}
\label{sec:RelationalPresentations}

\begin{wrapfigure}{r}{0.5\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.47\textwidth]{assets/final/VisualDependency}
    } 
\vspace{-5pt}
  \caption{Visualization of Dependencies}
  \label{fig:visualDependency}
\vspace{-24pt}
  \end{center}
\end{wrapfigure}

\ednote{meaning of moving right and down.}
\ednote {path of going through the slides - identify didactic things!!}
\ednote{show possible paths thru presentation}
\ednote{structuring of the presentation - link with primitives and spatial narrative}
\ednote{add example in slides and explain the different levels again}
\ednote {explain ids of slides}
\ednote{refer back to primitives: However, the relations can be much more expressive within impress.js.}

%impress.js gives us all the necessary primitives that were outlined in section \ref{sec:primitives}.

%into an interactive presentation.

@@

@@

@@

@@
